---
title: "Team Project Tracker"
subtitle: "EMSE 6035 · Marketing Analytics for Design Decisions · GWU · Fall 2026"
toc: false
---

```{r}
#| label: setup
source(file.path("R", "helpers.R"))
deadlines  <- read_data("deadlines.csv")
activities <- read_data("activities.csv")
weeks      <- read_data("weeks.csv")

next_project <- deadlines |>
  filter(kind == "project", date >= today) |>
  arrange(date) |>
  slice(1)

deliv <- deliverables(deadlines)
n_deliv_done <- sum(status_slug(deliv$state) == "done")

acts_done  <- sum(status_slug(activities$status) == "done")
acts_total <- nrow(activities)
pct_done   <- round(100 * acts_done / acts_total)

open_crit <- activities |>
  filter(critical, status_slug(status) != "done") |>
  arrange(due) |>
  slice_head(n = 6)

upcoming <- deadlines |>
  filter(date >= today) |>
  arrange(date) |>
  slice_head(n = 8)
```

One page that knows where the team project stands: what is due next, which activities are on the critical path, how each week went, and a dev log of every work session. Everything on this site is generated from three CSV files in `data/`; edit those, re-render, push.

::: {.status-strip}
::: {.status-card}
<div class="label">Rendered</div>
<div class="value">`r fmt_date(today, "%b %e")`</div>
<div class="sub">`r format(today, "%A, %Y")`</div>
:::
::: {.status-card}
<div class="label">Semester week</div>
<div class="value">`r semester_week()` of 16</div>
<div class="sub">`r if (semester_week() < 16) paste(as.integer(semester_end - today), "days to the end") else "final week"`</div>
:::
::: {.status-card}
<div class="label">Next project deliverable</div>
<div class="value">`r if (nrow(next_project)) fmt_date(next_project$date) else "none"`</div>
<div class="sub">`r if (nrow(next_project)) paste0(next_project$item, ", ", when_label(next_project$date)) else "all deliverables past"`</div>
:::
::: {.status-card}
<div class="label">Deliverables submitted</div>
<div class="value">`r n_deliv_done` of `r nrow(deliv)`</div>
<div class="sub">45 percent of the course grade</div>
:::
::: {.status-card}
<div class="label">Activities done</div>
<div class="value">`r acts_done` of `r acts_total`</div>
<div class="sub">`r pct_done` percent of the activity list</div>
:::
:::

<div class="progress-bar-wrap"><div class="progress-bar-fill" style="width: `r pct_done`%"></div></div>

## Next up

Every dated item in the next stretch, from the course calendar. Project deliverables are the ones this site exists for; homework and quizzes are shown because they compete for the same weeks.

```{r}
upcoming |>
  transmute(
    When  = paste0(fmt_date(date), " <small class='text-muted'>(", when_label(date), ")</small>"),
    Kind  = kind_pill(kind),
    Item  = item,
    Where = replace_na(where, ""),
    State = pill(state)
  ) |>
  nice_table(align = "llllc")
```

## Deliverable pipeline

Seven deliverables, all submitted by pushing to the team's GitHub repo by 11:59 pm on the tracked date (the course overview table shows a date one day later for most of them; the earlier date is the one tracked here).

```{r}
deliv |>
  transmute(
    `#` = n,
    Deliverable = str_remove(item, " \\(.*\\)$"),
    Due = fmt_date(date, "%a %b %e"),
    When = when_label(date),
    `Weight (%)` = weight_pct,
    State = pill(state),
    Notes = replace_na(notes, "")
  ) |>
  nice_table(align = "rlllccl")
```

## On the critical path right now

The next open activities that sit on the [critical path](tracker/critical-path.qmd). If one of these slips, the deliverable behind it slips.

```{r}
open_crit |>
  transmute(
    ID = id,
    Phase = phase,
    Activity = activity,
    Owner = owner,
    Due = paste0(fmt_date(due), " <small class='text-muted'>(", when_label(due), ")</small>"),
    Status = pill(status)
  ) |>
  nice_table(align = "llllll")
```

## This week

```{r}
#| results: asis
wk <- weeks |> filter(week == semester_week())
if (nrow(wk) == 1) {
  cat(sprintf(
    "**Week %d (class on %s): %s.** %s Project focus: %s. %s\n",
    wk$week, fmt_date(wk$date), wk$class_topic,
    ifelse(is.na(wk$quiz) | wk$quiz == "", "", paste0("Quiz: ", wk$quiz, ". ")),
    wk$project_focus,
    ifelse(is.na(wk$progress_note) | wk$progress_note == "", "", paste0("Progress note: ", wk$progress_note, "."))
  ))
} else {
  cat("Outside the semester calendar.\n")
}
```

See the full [week-by-week table](tracker/progress.qmd), the [activity list](tracker/activities.qmd), and the [dev log](devlog/index.qmd) for what happened in each work session.
