---
title: "Team Project Tracker"
subtitle: "EMSE 6035 · Marketing Analytics for Design Decisions · GWU · Fall 2026 · Team E · Smart Urban Living"
toc: false
---

```{r}
#| label: setup
source(file.path("R", "helpers.R"))
deadlines  <- read_data("deadlines.csv")
weeks      <- read_data("weeks.csv")
sched      <- cpm(read_activities())
health     <- schedule_health(sched)

deliv <- deliverables(deadlines)
n_deliv_done <- sum(status_slug(deliv$state) == "done")

next_project <- deliv |> filter(date >= today) |> arrange(date) |> slice(1)
next_days <- if (nrow(next_project)) days_until(next_project$date) else NA

work <- sched |> filter(phase != "Ongoing")
acts_done  <- sum(status_slug(work$status) == "done")
acts_total <- nrow(work)

open_crit <- sched |>
  filter(status_slug(status) != "done", critical) |>
  arrange(es, id)
open_near <- sched |> filter(status_slug(status) != "done", near_critical)
overdue   <- sched |> filter(overdue)

upcoming <- deadlines |>
  filter(date >= today) |>
  arrange(date) |>
  slice_head(n = 8)

spi_word <- dplyr::case_when(
  is.na(health$spi) ~ "no plan yet",
  health$spi >= 0.97 ~ "on plan",
  health$spi >= 0.85 ~ "slightly behind",
  TRUE ~ "behind plan"
)
```

<p class="hero-lead">One page that knows where the team project stands. The schedule below is not typed in: every render runs a critical path method over <code>data/activities.csv</code> (early and late dates, total float, the zero-float chain) with today as the status date, so the numbers move as the CSV changes.</p>

::: {.status-strip}
::: {.status-card .is-hero}
<div class="label">Next deliverable</div>
<div class="value">`r if (nrow(next_project)) paste0(next_days, " <small>days</small>") else "none"`</div>
<div class="sub">`r if (nrow(next_project)) paste0(str_remove(next_project$item, " \\(.*\\)$"), ", due ", fmt_date(next_project$date), " (", next_project$weight_pct, " percent of the grade)") else "all deliverables past"`</div>
:::
::: {.status-card}
<div class="label">Schedule health</div>
<div class="value">`r health$earned_pct`%</div>
<div class="sub">Earned activity-days; the plan says `r health$planned_pct`% by today. `r str_to_sentence(spi_word)` (index `r health$spi`)</div>
:::
::: {.status-card}
<div class="label">Zero float, open now</div>
<div class="value">`r nrow(open_crit)`</div>
<div class="sub">`r nrow(open_near)` more with 1 to 3 days; `r nrow(overdue)` overdue</div>
:::
::: {.status-card}
<div class="label">Deliverables submitted</div>
<div class="value">`r n_deliv_done` <small>of `r nrow(deliv)`</small></div>
<div class="sub">45 percent of the course grade</div>
:::
::: {.status-card}
<div class="label">Semester week</div>
<div class="value">`r semester_week()` <small>of 16</small></div>
<div class="sub">`r fmt_date(today)`; `r acts_done` of `r acts_total` activities done</div>
:::
:::

<div class="meter"><div class="meter-fill" style="width: `r health$earned_pct`%"></div><div class="meter-mark" style="left: `r health$planned_pct`%"></div></div>
<div class="meter-caption"><span>Earned `r health$earned_pct`% of planned activity-days</span><span>Plan says `r health$planned_pct`% by today (the mark)</span></div>

## The next four weeks

Open activities with a computed early start inside the window. Solid is done, the hatched tint is what remains, a diamond is an official deadline, the red edge marks zero float. Hover any row for the early and late dates; click a row to light up everything it depends on and everything waiting on it.

```{r}
#| results: asis
embed_schedule(sched, deadlines, weeks)
cat('<div data-tracker="gantt" data-mode="open" data-window="next4" data-controls="false" data-load="true"></div>')
```

## On the zero-float chain right now

If any of these slip by a day, the deliverable behind them slips by a day. The [critical path](tracker/critical-path.qmd) page shows the whole chain.

```{r}
open_crit |>
  slice_head(n = 8) |>
  transmute(
    ID = id,
    Phase = phase_dot(phase),
    Activity = activity,
    Owner = owner,
    `Early start` = paste0(fmt_date(es), " <small class='text-muted'>(", when_label(es), ")</small>"),
    `Must finish` = fmt_date(lf),
    Float = float_pill(total_float, status),
    Status = pill(status)
  ) |>
  nice_table(align = "lllllllc")
```

## Deliverable chain

Each box is an official deadline. The label on the arrow is the smallest float left in the work feeding that deadline; red means none.

```{r}
#| results: asis
cat('<div data-tracker="chain"></div>')
```

## Due next

Every dated item in the next stretch, from the course calendar. Project deliverables are the ones this site exists for; homework and quizzes are shown because they compete for the same weeks.

```{r}
upcoming |>
  transmute(
    When  = paste0(fmt_date(date), " <small class='text-muted'>(", when_label(date), ")</small>"),
    Kind  = kind_pill(kind),
    Item  = item,
    Where = replace_na(where, ""),
    State = pill(state)
  ) |>
  nice_table(align = "llllc")
```

## This week

```{r}
#| results: asis
wk <- weeks |> filter(week == semester_week())
if (nrow(wk) == 1) {
  cat(sprintf(
    "**Week %d (%s): %s.** %sProject focus: %s. %s\n",
    wk$week, fmt_date(wk$date), wk$class_topic,
    ifelse(is.na(wk$quiz) | wk$quiz == "", "", paste0("Quiz: ", wk$quiz, ". ")),
    wk$project_focus,
    ifelse(is.na(wk$progress_note) | wk$progress_note == "", "", paste0("Progress note: ", wk$progress_note, "."))
  ))
} else {
  cat("Outside the semester calendar.\n")
}
```

See the full [schedule](tracker/schedule.qmd), the [activity list](tracker/activities.qmd), the [risk register](tracker/risks.qmd), the [week-by-week table](tracker/progress.qmd), and the [dev log](devlog/index.qmd) for what happened in each work session.
