---
title: "Deadlines"
subtitle: "Every dated item of the semester, from data/deadlines.csv"
---

```{r}
source(file.path("R", "helpers.R"))
deadlines <- read_data("deadlines.csv") |> arrange(date)
```

All homework and project deliverables are due by 11:59 pm on the date shown. Homework dates are the ones printed on the course schedule page (checked Sep 16): mostly Mondays, with HW1 on a Sunday, HW3 on a Friday, and HW12 and HW13 on Sundays. Where the course overview table shows a project date one day later than the schedule page, the earlier date is tracked. This table is the whole of `data/deadlines.csv`; the `state` column is the team's to update.

## Filter by kind

```{r}
#| results: asis
kinds <- c("project", "homework", "quiz", "exam", "class")
counts <- deadlines |> count(kind) |> deframe()
cat(paste(sprintf("%s: %d", kind_pill(kinds), counts[kinds]), collapse = " &nbsp; "))
```

## Full calendar

```{r}
deadlines |>
  transmute(
    Date = fmt_date(date, "%a %b %e"),
    When = when_label(date),
    Kind = kind_pill(kind),
    Item = item,
    `Weight (%)` = ifelse(is.na(weight_pct), "", as.character(weight_pct)),
    Where = replace_na(where, ""),
    State = pill(state),
    Notes = replace_na(notes, "")
  ) |>
  nice_table(align = "lllllllcl")
```

## Project deliverables only

```{r}
deliverables(deadlines) |>
  transmute(
    `#` = n,
    Deliverable = item,
    Due = fmt_date(date, "%A, %B %e"),
    When = when_label(date),
    `Weight (%)` = weight_pct,
    State = pill(state),
    Notes = replace_na(notes, "")
  ) |>
  nice_table(align = "rlllccl")
```
