---
title: "Activities"
subtitle: "Every task between now and the final presentation, by phase"
---

```{r}
source(file.path("R", "helpers.R"))
activities <- read_data("activities.csv") |>
  mutate(phase = factor(phase, levels = c(
    "Setup", "Proposal", "Survey plan", "Pilot survey", "Pilot analysis",
    "Final survey", "Final analysis", "Presentation", "Ongoing"
  )))
```

The activity list lives in `data/activities.csv`. Each row has an `id`, a `phase`, an `owner`, a `start` and `due` date, the ids it `depends_on`, whether it sits on the `critical` path, and a `status` (Not started, In progress, Done, Blocked, Dropped). To change anything, edit the CSV, re-render, and push; the tables below and the home page dashboard update themselves.

## Summary by phase

```{r}
activities |>
  group_by(Phase = phase) |>
  summarise(
    Activities = n(),
    Done = sum(status_slug(status) == "done"),
    `In progress` = sum(status_slug(status) == "active"),
    `Not started` = sum(status_slug(status) == "todo"),
    `First due` = fmt_date(min(due)),
    `Last due` = fmt_date(max(due)),
    .groups = "drop"
  ) |>
  nice_table(align = "lrrrrll")
```

## Overdue or due within 14 days

```{r}
soon <- activities |>
  filter(status_slug(status) != "done", days_until(due) <= 14) |>
  arrange(due)
if (nrow(soon) == 0) {
  cat("Nothing open is due in the next two weeks.")
} else {
  soon |>
    transmute(
      ID = id, Phase = phase, Activity = activity, Owner = owner,
      Due = paste0(fmt_date(due), " <small class='text-muted'>(", when_label(due), ")</small>"),
      Status = pill(status)
    ) |>
    nice_table(align = "llllll")
}
```

## Full list

```{r}
#| results: asis
for (ph in levels(activities$phase)) {
  block <- activities |> filter(phase == ph) |> arrange(due, id)
  if (nrow(block) == 0) next
  cat("\n\n### ", ph, "\n\n", sep = "")
  tbl <- block |>
    transmute(
      ID = id,
      Activity = activity,
      Owner = owner,
      Start = fmt_date(start),
      Due = fmt_date(due),
      `Depends on` = replace_na(depends_on, ""),
      Critical = ifelse(critical, "yes", ""),
      Status = pill(status),
      Deliverable = replace_na(deliverable, ""),
      Notes = replace_na(notes, "")
    ) |>
    nice_table(align = "lllllllcll")
  cat(as.character(tbl))
}
```
