---
title: "Activities"
subtitle: "Every task between now and the final presentation, by phase, with the computed dates beside the planned ones"
---

```{r}
source(file.path("R", "helpers.R"))
sched <- cpm(read_activities())
```

The activity list lives in `data/activities.csv`. Each row has an `id`, a `phase`, an `owner`, a planned `start` and `due`, an optional hard `deadline` (the official due date), the ids it `depends_on`, a `status` (Not started, In progress, Done, Blocked, Dropped) and a `pct` complete. Everything else on this page, early and late dates, float, the critical flag, is computed by `cpm()` in `R/helpers.R` when the site renders. To change anything, edit the CSV, re-render, push.

## Summary by phase

```{r}
sched |>
  group_by(Phase = phase) |>
  summarise(
    Activities = n(),
    Done = sum(status_slug(status) == "done"),
    `In progress` = sum(status_slug(status) == "active"),
    `Not started` = sum(status_slug(status) == "todo"),
    `Zero float` = sum(critical & status_slug(status) != "done"),
    `Earliest start` = fmt_date(min(es)),
    `Latest finish` = fmt_date(max(ef)),
    .groups = "drop"
  ) |>
  mutate(Phase = phase_dot(Phase)) |>
  nice_table(align = "lrrrrrll")
```

## Overdue or starting within 14 days

```{r}
soon <- sched |>
  filter(status_slug(status) != "done", phase != "Ongoing", overdue | days_until(es) <= 14) |>
  arrange(es, id)
if (nrow(soon) == 0) {
  cat("Nothing open starts in the next two weeks.")
} else {
  soon |>
    transmute(
      ID = id, Phase = phase_dot(phase), Activity = activity, Owner = owner,
      `Early start` = paste0(fmt_date(es), " <small class='text-muted'>(", when_label(es), ")</small>"),
      `Early finish` = fmt_date(ef),
      Float = float_pill(total_float, status),
      Status = pill(status)
    ) |>
    nice_table(align = "llllllcc")
}
```

## Full list

Planned dates are what the team wrote down; early dates are what the dependencies and today's date allow. When the two differ, a predecessor is holding the activity back.

```{r}
#| results: asis
for (ph in levels(sched$phase)) {
  block <- sched |> filter(phase == ph) |> arrange(es, id)
  if (nrow(block) == 0) next
  cat("\n\n### ", ph, "\n\n", sep = "")
  tbl <- block |>
    transmute(
      ID = id,
      Activity = activity,
      Owner = owner,
      Planned = paste0(fmt_date(start, "%b %e"), " to ", fmt_date(due, "%b %e")),
      Early = paste0(fmt_date(es, "%b %e"), " to ", fmt_date(ef, "%b %e")),
      Deadline = fmt_date(deadline, "%b %e"),
      `Depends on` = str_replace_all(replace_na(depends_on, ""), ";", ", "),
      Float = float_pill(total_float, status),
      Status = pill(status),
      `%` = pct,
      Notes = replace_na(notes, "")
    ) |>
    nice_table(align = "lllllllccrl")
  cat(as.character(tbl))
}
```
