---
title: "Requirements"
subtitle: "Every rubric criterion the course grades, the activities that carry it, and how far along each is"
toc: false
---

```{r}
source(file.path("R", "helpers.R"))
req   <- read_data("requirements.csv")
sched <- cpm(read_activities())
by_id <- setNames(split(sched, seq_len(nrow(sched))), sched$id)

status_of <- function(ids) {
  ids <- trimws(str_split(ids, ";")[[1]])
  missing <- ids[!ids %in% sched$id]
  if (length(missing)) return(list(label = paste("missing:", paste(missing, collapse = ", ")), slug = "blocked", pct = 0))
  rows <- sched |> filter(id %in% ids)
  slugs <- status_slug(rows$status)
  pct <- round(100 * sum(rows$pct / 100 * rows$dur) / sum(rows$dur))
  if (all(slugs == "done")) list(label = "Done", slug = "done", pct = 100)
  else if (any(slugs %in% c("done", "active"))) list(label = sprintf("In progress (%d%%)", pct), slug = "active", pct = pct)
  else list(label = "Not started", slug = "todo", pct = 0)
}
st <- lapply(req$activities, status_of)
req <- req |>
  mutate(
    status_label = map_chr(st, "label"),
    status_slug  = map_chr(st, "slug"),
    earliest = map_chr(activities, function(a) {
      ids <- trimws(str_split(a, ";")[[1]])
      rows <- sched |> filter(id %in% ids)
      if (!nrow(rows)) "" else fmt_date(min(rows$es), "%b %e")
    }),
    latest = map_chr(activities, function(a) {
      ids <- trimws(str_split(a, ";")[[1]])
      rows <- sched |> filter(id %in% ids)
      if (!nrow(rows)) "" else fmt_date(max(rows$ef), "%b %e")
    }),
    crit = map_lgl(activities, function(a) {
      ids <- trimws(str_split(a, ";")[[1]])
      any(sched$critical[sched$id %in% ids] & status_slug(sched$status[sched$id %in% ids]) != "done")
    })
  )
unmapped <- req |> filter(status_slug == "blocked")
graded <- req |> filter(points > 0)
```

The course grades seven deliverables on `r sum(graded$points)` rubric points (45 percent of the final grade). This page is the traceability check: each criterion from the course's deliverable pages, in `data/requirements.csv`, points at the activity ids in `data/activities.csv` that produce it. A criterion with no live activity would show as missing; today `r if (nrow(unmapped) == 0) "none is" else paste(nrow(unmapped), "are")`.

## By deliverable

```{r}
graded |>
  group_by(Deliverable = deliverable) |>
  summarise(
    Criteria = n(),
    Points = sum(points),
    Done = sum(status_slug == "done"),
    `In progress` = sum(status_slug == "active"),
    `Not started` = sum(status_slug == "todo"),
    `On zero float` = sum(crit),
    .groups = "drop"
  ) |>
  mutate(Deliverable = factor(Deliverable, levels = c("Proposal", "Survey plan", "Pilot survey", "Pilot analysis", "Final survey", "Final analysis", "Presentation"))) |>
  arrange(Deliverable) |>
  nice_table(align = "lrrrrrr")
```

## Every criterion

```{r}
#| results: asis
for (d in c("Proposal", "Survey plan", "Pilot survey", "Pilot analysis", "Final survey", "Final analysis", "Presentation", "Every deliverable")) {
  block <- req |> filter(deliverable == d)
  if (!nrow(block)) next
  pts <- sum(block$points)
  cat("\n\n### ", d, if (pts > 0) sprintf(" (%d points)", pts) else "", "\n\n", sep = "")
  tbl <- block |>
    transmute(
      ID = id,
      Criterion = criterion,
      Points = ifelse(points > 0, as.character(points), ""),
      `What it needs` = needs,
      Activities = str_replace_all(activities, ";", ", "),
      Window = ifelse(earliest == "", "", paste0(earliest, " to ", latest)),
      Status = sprintf('<span class="pill pill-%s">%s</span>', status_slug, status_label)
    ) |>
    nice_table(align = "llrlllc", class = "req-table")
  cat(as.character(tbl))
}
```

## Where the course pages and the plan differ

- The proposal page does not cap the number of attributes ("the major product attributes you will include"); six is allowed, and it asks that the attribute table also show competitors' features, which is why v2 names real products.
- The survey plan page sets Prolific's U.S. general population as the default distribution; the draft proposal names the GWU community and networks. Decision D07 on the [project](../context-bank/project.qmd) page; settled in SP02.
- The pilot and final survey rubrics score deployment under "surveydown": the survey must render, be completable to the end, and store responses. PS04 and PS05 (and FS02) carry that; an end-to-end test on a phone is part of both.
- The final presentation page still shows last year's date in its title-slide instruction; the class date this year is Wednesday Dec 9, and slides are due Tuesday Dec 8.
