---
title: "Critical path"
subtitle: "The chain of activities that cannot slip without moving a deliverable, computed on every render"
toc: false
---

```{r}
source(file.path("R", "helpers.R"))
deadlines <- read_data("deadlines.csv")
weeks     <- read_data("weeks.csv")
sched     <- cpm(read_activities())

open <- sched |> filter(status_slug(status) != "done", phase != "Ongoing")
crit <- open |> filter(critical) |> arrange(es, id)
near <- open |> filter(near_critical) |> arrange(es, id)
slack <- open |> filter(!critical, !near_critical, !is.na(total_float)) |> arrange(es, id)
```

The project is a strict pipeline: each deliverable is the input to the next, and the final survey has to be in the field over Thanksgiving before any final analysis can happen. Because every submission date is a hard constraint, the critical path is not one long chain but a series of zero-float segments, one per deliverable, joined by the handoffs between them. Today `r nrow(crit)` open activities carry zero float, `r nrow(near)` carry one to three days, and `r nrow(slack)` have more room than that.

## The chain

```{r}
#| results: asis
embed_schedule(sched, deadlines, weeks)
cat('<div data-tracker="chain"></div>')
```

## Only the critical path

The same Gantt as the [schedule](schedule.qmd) page, filtered to the open activities with zero float. Hover for early and late dates; click a row to see what feeds it and what waits on it.

```{r}
#| results: asis
cat('<div data-tracker="gantt" data-mode="critical" data-window="semester" data-controls="false" data-load="false"></div>')
```

## Float on every open activity

Early start and finish come from the forward pass; late start and finish from the backward pass off the official deadlines. Total float is the gap between them. Free float is how far the activity can slip before it delays its immediate successor rather than a deadline.

```{r}
open |>
  filter(!is.na(total_float)) |>
  arrange(total_float, es, id) |>
  transmute(
    ID = id,
    Phase = phase_dot(phase),
    Activity = activity,
    `Early` = paste0(fmt_date(es, "%b %e"), " to ", fmt_date(ef, "%b %e")),
    `Late`  = paste0(fmt_date(ls, "%b %e"), " to ", fmt_date(lf, "%b %e")),
    `Deadline` = fmt_date(deadline, "%b %e"),
    `Total float` = float_pill(total_float, status),
    `Free float` = ifelse(is.na(free_float), "", paste0(free_float, " d")),
    `Feeds into` = str_replace_all(successors, ";", ", "),
    Status = pill(status)
  ) |>
  nice_table(align = "lllllllllc")
```

## Where the risk concentrates

Three places have no give at all. **This week**: the proposal workshop, the revision and the move into the official repo all sit between today and Sunday with zero float, because the meeting and the deadline share the week. **Weeks 9 to 11**: the pilot exchange on Oct 21 feeds a Nov 1 report through a chain of two-day tasks, and the final survey has to be rebuilt and redeployed by Nov 15 with one day of float, while HW8 to HW10 and Quiz 5 land in the same fortnight. **Thanksgiving to Dec 6**: the Prolific data arrives at the end of the assumed fielding window and the final report is due the Sunday after the in-class exam, so cleaning, modelling, analysis and writing each get about two days.

The defences are already in the plan: start cleaning on partial pilot data (PA02) while the feedback is triaged in parallel (PA05); scaffold every final-analysis script and the report skeleton on the pilot data in the second week of November (FA01, six days of float, so it can absorb a slip without hurting anything); confirm the Prolific launch date at the Nov 11 class so FS04 stops being an assumption. The [risk register](risks.qmd) carries the triggers and responses.
